### 2015-02-28 icfp15-servo/open.tex
Clarify unsafe code issues, per jdm

\paragraph{Unsafe code correctness.} Today, when we write unsafe code in Rust
there is limited validation of memory lifetimes or type safety within that
code block.
However, many of our uses of unsafe code are well-behaved pointer lifetime
or memory translations that cannot be annotated or inferred in Rust.
We are very interested in additional annotations that would help us prove
basic properties about our unsafe code, even if these annotations require a
theorem prover or ILP solver to check.

>>>>

\paragraph{Unsafe code correctness.} Today, when we write unsafe code in Rust
there is limited validation of memory lifetimes or type safety within that
code block.
However, many of our uses of unsafe code are well-behaved translations of
either pointer lifetimes or data representations that cannot be annotated
or inferred in Rust.
We are very interested in additional annotations that would help us prove
basic properties about our unsafe code, even if these annotations require a
theorem prover or ILP solver to check.
